\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\large{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Koichi Kimura} \\ \vspace{1pt}
    \textbf{\Large \scshape Frontend React Developer} \\
    % 電話番号とアドレス。応募先が居住国外ならなら国際番号(例: +1)も入れるか電話番号は消してしまう
    \large 236 308-2236 $|$ Vancouver, Canada
\end{center}

\begin{center}
% Emailをhrefとunderline内に
    \href{mailto:Insert your email}{\underline{tech.kupumaru@gmail.com}} $|$ 
% LinkedInのリンク
    \href{https://www.linkedin.com/in/koichi-kimura-06ba14259/}{\underline{linkedin.com/in/koichi-kimura-06ba14259}} $|$
% Githubのリンク
    \href{https://github.com/kupuma-ru21}{\underline{https://github.com/kupuma-ru21}}
\end{center}

\section{About}
Software Engineer with 4 years of experience and a love of learning new skills.
My strong suits are Typescript, React, Next.js.
I've used Typescript and React for about four years, and Next.js for about two years.
I've already used App router by Next.js at work.
I'm strongly interested in maintainability of source codes and design patterns.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Frontend and Backend Developer}{Feb 2023 - Dec 2023}
      {BUYSELL TECHNOLOGIES}{Tokyo, Japan(Remote}
      \begin{itemize}
        \resumeItem{Selected and introduced some libs.}
        \resumeItem{Observed errors notifications from sentry and fixed them.}
        \resumeItem{Created resolver of graphql with golang.}
      \end{itemize}
      {Used Technologies: react.js, next.js, storybook, graphql, graphql-codegen, apollo/client, material-ui, react-hook-form, zod, vitest, esLint, prettier, pnpm, git, slack, jira, figma, golang, sqlboiler}

    \resumeSubheading
      {Frontend Developer}{May 2021 - Feb 2023}
      {VISITS TECHNOLOGIES}{Tokyo, Japan(Remote}
      \begin{itemize}
        \resumeItem{Improved developer experiences by installing eslint prettier etc.}
        \resumeItem{Reviewed pull requests from my coworkers.}
        \resumeItem{Created test codes with jest and react-testing-library}
        \resumeItem{Updated React v17 to v18.}
      \end{itemize}
      {Used Technologies: react.js, react-router, react-datepicker, react-dnd, react-i18next, react-testing-library, graphql, graphql-codegen, apollo/client, styled-components, react-hook-form, yup, react-i18next, jest, echarts, koa, esLint, prettier, yarn, git, slack, jira, figma}

    \resumeSubheading
      {Frontend Developer}{Sep 2019 - May 2021}
      {Gizmo inc.}{Tokyo, Japan}
      \begin{itemize}
        \resumeItem{Created UI and business logic for logistics web application used by SoftBank with Vue.js.}
        \resumeItem{Created UI and business logic for internet bank web application released by SONY with React.js.}
        \resumeItem{Technically supported my coworkers.}
      \end{itemize}
      {Used Technologies: react.js, redux, react-redux, reselect, styled-components, next.js, formik, yup, react-i18next, @adobe/target-react-component, axios, immer, ramda, redux-logger, redux-saga, typesafe-actions, dotenv-webpack, prism, jest, eslint, yarn, git, gitlab, aws, codecommit, sourcetree, slack, adobe xd, vue.js, vue router, vuex, vuetify, axios, joi, lodash, veeValidate, github}

  \resumeSubHeadingListEnd

%
%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, HTML/CSS, React, Vue, Golang} \\
     \textbf{Frameworks}{: React (library), Next.js, Storybook} \\
     \textbf{Developer Tools}{: Git, Docker, Github Actions} \\
    }}
 \end{itemize}

 %-----------Education-----------
\section{Education}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Bachelor of engineering}{: Takushoku University, Tokyo, Japan (Apr 2015 - Mar 2019)} \\
     \textbf{Web development diploma}{: Cornerstone International College, Vancouver (May 2024 -)} \\
    }}
 \end{itemize}

 %-----------LANGUAGES-----------
\section{LANGUAGES}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English - Upper-intermediate} \\
     \textbf{Japanese - Native} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
